\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=3cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fancyhdr}
\usepackage{seminar}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}
\usepackage{hyperref}

\pagestyle{fancy}


%You can add theorem-like environments (e.g. remark, definition, ...) if you want
\newtheorem{theorem}{Theorem}

\title{Can you hear the shape, style, and correspondence of a drum?}
\author{Sricharan Chiruvolu} % Replace with your name
\institute{Department of Informatics - Technische Universit\"{a}t M\"{u}nchen} % Replace with the department you belong to

\makeatletter
\let\runauthor\@author
\let\runtitle\@title
\makeatother
\lhead{\runauthor}
\rhead{\runtitle}




\begin{document}

\maketitle

\begin{abstract}
Write a brief abstract here (around 150 words).
\end{abstract}

\section{A few remarks}

Each report should include an introduction describing the problem, the motivations and a brief outline. The main approach should then be described and discussed in separate sections, followed by experimental results (when applicable) and conclusions.

\begin{itemize}
\item You are not expected to implement the methods described in the paper you have been assigned. Nevertheless, figures demonstrating some results are very welcome and can be directly copy-pasted from other sources.
\item Please use citations when appropriate. Again, you are not expected to read through all the references appearing in your assigned paper. Add your citations in bibtex format into the file egbib.bib. An example is \cite{dijkstra59}.
\item You can use the theorem environment to write theorems. An example:
\begin{theorem}
\label{mytheorem}
Let $p$ be a prime number. Then, for any $a \in \mathbb{N}$, $a^p - a$ is evenly divisible by $p$. More formally,
\begin{equation}
a^p \equiv a \, (\mathrm{mod}\, p)\,.
\end{equation}
\end{theorem}
\item Please keep all your formulas numbered.
\item The report should be 6 to 10 pages long (not including citations).
\item You can write your report in German if you want, but English is preferred.
\item Please do not change the layout ({\em e.g.}, do not change page margins, font size, etc.).
\end{itemize}
	
\bibliographystyle{plain}
\bibliography{egbib}



\end{document}
